---
title: \Large{Reported vs reproduced effect size estimates, separated by meta-analysis}
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height=4) 
library(readxl);library(ggplot2);library(gridExtra)
df <- read_excel("C:/Users/s421506/tiu/research/effectsizes/codebooks/codebook-primary-studies-final-complete.xlsx")
number_ticks <- function(n) {function(limits) pretty(limits, n)}
#change ordering of categories to no disc - not enough info - diff - ambiguous
for (i in 1:nrow(df)) {
  if (df$info[i] == 1) {
    df$info[i] <- "a"
  }
  if (df$info[i] == 2) {
    df$info[i] <- 1
  }
  if (df$info[i] == "a") {
    df$info[i] <- 2
  }
}

```

```{r MA1, echo=FALSE}
# Adesope
dfma <- subset(df, meta=="Adesope")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 12, 60%", "Different effect, k = 3, 15%", "Ambiguous effect, k = 5, 25%")
subheader <- paste("MA1: Adesope & Nesbit (k = 20)")
mycolors <- c("#FFFFFF", "#FFa500", "#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1) 
```
&nbsp;
&nbsp;
&nbsp;

```{r MA2, echo=FALSE}
# Alfieri
dfma <- subset(df, meta=="Alfieri")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 5, 25%", "Not enough information, k = 1, 5%", "Different effect, k = 4, 20%", "Ambiguous effect, k = 10, 50%")
subheader <- paste("MA2: Alfieri et al. (k = 20)")
mycolors <- c("#FFFFFF", "#FFFF00", "#FFa500", "#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) + 
  expand_limits(x = c(-2.3, 0.8)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1) 
```


```{r MA3, echo=FALSE}
# Babbage
dfma <- subset(df, meta=="Babbage")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 10, 91%", "Not enough information, k = 1, 9%")
subheader <- paste("MA3: Babbage et al. (k = 11)")
mycolors <- c("#FFFFFF", "#FFFF00")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA4, echo=FALSE}
# Balliet
dfma <- subset(df, meta=="Balliet")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 14, 67%", "Not enough information, k = 1, 5%", "Different effect, k = 4, 19%", "Ambiguous effect, k = 2, 10%")
subheader <- paste("MA4: Balliet et al. (k = 21)")
mycolors <- c("#FFFFFF", "#FFFF00", "#FFa500", "#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```


```{r MA5, echo=FALSE}
# Benish
dfma <- subset(df, meta=="Benish")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("Not enough information, k = 1, 9%", "Ambiguous effect, k = 10, 91%")
subheader <- paste("MA5: Benish et al. (k = 11)")
mycolors <- c("#FFFF00","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x = c(0,2), y = c(0, 2)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA6, echo=FALSE}
# Berry1 
dfma <- subset(df, meta=="Berry 1")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 1, 9%", "Different effect, k = 10, 91%")
subheader <- paste("MA6: Berry, Carpenter & Barrat (k = 11)")
mycolors <- c("#FFFFFF","#FFa500")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(y = c(0, 0.7), x = c(0,0.7)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA7, echo=FALSE}
# Berry2
dfma <- subset(df, meta=="Berry 2")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 21, 91%", "Different effect, k = 1, 4%", "Ambiguous effect, k = 1, 4%")
subheader <- paste("MA7: Berry, Clark, & McClure (k = 23)")
mycolors <- c("#FFFFFF","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```


&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA8, echo=FALSE}
# Card
dfma <- subset(df, meta=="Card")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 5, 56%", "Not enough information, k = 2, 22%","Different effect, k = 1, 11%", "Ambiguous effect, k = 1, 11%")
subheader <- paste("MA8: Card et al. (k = 9)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x = c(-0.12, 0.12),y = c(-0.12, 0.12)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```


```{r MA9, echo=FALSE}
# Crook
dfma <- subset(df, meta=="Crook")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 17, 77%", "Different effect, k = 2, 9%", "Ambiguous effect, k = 3, 14%")
subheader <- paste("MA9: Crook et al. (k = 22)")
mycolors <- c("#FFFFFF","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA10, echo=FALSE}
# de Wit
dfma <- subset(df, meta=="de Wit")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 17, 81%", "Different effect, k = 3, 14%", "Ambiguous effect, k = 1, 5%")
subheader <- paste("MA10: de Wit et al. (k = 21)")
mycolors <- c("#FFFFFF","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```




```{r MA11, echo=FALSE}
# Else-Quest
dfma <- subset(df, meta=="Else-quest")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 5, 25%", "Not enough information, k = 8, 40%", "Ambiguous effect, k = 7, 35%")
subheader <- paste("MA11: Else-Quest et al. (k = 20)")
mycolors <- c("#FFFFFF","#FFFF00","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Cohen's d)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Cohen's d)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)

```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA12, echo=FALSE}
# Farber 
dfma <- subset(df, meta=="Farber")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 1, 9%", "Different effect, k = 1, 9%", "Ambiguous effect, k = 9, 82%")
subheader <- paste("MA12: Farber & Doolin (k = 11)")
mycolors <- c("#FFFFFF","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(y = c(0,0.85), x = c(0,0.85)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)

```

```{r MA13, echo=FALSE}
# Fischer
dfma <- subset(df, meta=="Fischer")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 15, 75%", "Different effect, k = 3, 15%", "Ambiguous effect, k = 2, 10%")
subheader <- paste("MA13: Fischer et al. (k = 20)")
mycolors <- c("#FFFFFF","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA14, echo=FALSE}
# Fox 
dfma <- subset(df, meta=="Fox")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 13, 65%","Not enough information, k = 1, 5%", "Different effect, k = 5, 25%", "Ambiguous effect, k = 1, 5%")
subheader <- paste("MA14: Fox et al. (k = 20)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA15, echo=FALSE}
# Freund
dfma <- subset(df, meta=="Freund")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 20, 100%")
subheader <- paste("MA15: Freund & Kasten (k = 20)")
mycolors <- c("#FFFFFF")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)

```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA16, echo=FALSE}
# Green
dfma <- subset(df, meta=="Green")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 5, 38%","Not enough information, k = 5, 38%","Different effect, k = 3, 23%")
subheader <- paste("MA16: Green & Rosenfeld (k = 13)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Cohen's d)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Cohens's d)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)

```

```{r MA17, echo=FALSE}
# Hallion
dfma <- subset(df, meta=="Hallion")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 3, 27%","Not enough information, k = 3, 27%", "Different effect, k = 2, 18%","Ambiguous effect, k = 3, 27%")
subheader <- paste("MA17: Hallion & Ruscio (k = 11)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x = c(-0.4,2.2), y=c(-0.4,2.2)) +
  annotate("text", x = -Inf, y = 2, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)

```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
```{r MA18, echo=FALSE}
# Ihle
dfma <- subset(df, meta=="Ihle")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 7, 50%","Not enough information, k = 3, 21%", "Different effect, k = 2, 14%","Ambiguous effect, k = 2, 14%")
subheader <- paste("MA18: Ihle et al. (k = 14)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x = c(-0.4,0.6), y=c(-0.4,0.6)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)

```


```{r MA19, echo=FALSE}
# Koenig
dfma <- subset(df, meta=="Koenig")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 8, 40%","Not enough information, k = 4, 20%", "Different effect, k = 5, 25%","Ambiguous effect, k = 3, 15%")
subheader <- paste("MA19: Koenig et al. (k = 20)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x = c(-1,3), y=c(-1,3)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)

```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;


```{r MA20, echo=FALSE}
# kolden
dfma <- subset(df, meta=="Kolden")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 1, 10%","Ambiguous effect, k = 9, 90%")
subheader <- paste("MA20: Kolden et al. (k = 10)")
mycolors <- c("#FFFFFF","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x=c(-0.25,0.7),y=c(-0.25,0.7)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA21, echo=FALSE}
# Lucassen
dfma <- subset(df, meta=="Lucassen")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 7, 64%","Not enough information, k = 3, 27%","Different effect, k = 1, 9%")
subheader <- paste("MA21: Lucassen et al. (k = 10)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA22, echo=FALSE}
# Mol
dfma <- subset(df, meta=="Mol")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 8, 100%")
subheader <- paste("MA22: Mol & Bus (k = 8)")
mycolors <- c("#FFFFFF")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Fisher's z)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Fisher's z)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA23, echo=FALSE}
# Morgan
dfma <- subset(df, meta=="Morgan")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 1, 11%","Not enough information, k = 6, 67%","Different effect, k = 1, 11%","Ambiguous effect, k = 1, 11%")
subheader <- paste("MA23: Morgan et al. (k = 9)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x=c(-0.85,1.8),y=c(-0.85,1.8)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA24, echo=FALSE}
#Munder
dfma <- subset(df, meta=="Munder")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 5, 31%","Not enough information, k = 1, 6%","Different effect, k = 1, 6%","Ambiguous effect, k = 9, 56%")
subheader <- paste("MA24: Munder et al. (k = 16)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA25, echo=FALSE}
#Piet
dfma <- subset(df, meta=="Piet")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 4, 50%","Not enough information, k = 2, 25%","Different effect, k = 2, 25%")
subheader <- paste("MA25: Piet et al. (k = 8)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.3), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x=c(0.1,1),y=c(0.1,1)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA26, echo=FALSE}
# Smith
dfma <- subset(df, meta=="Smith")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 14, 67%","Different effect, k = 3, 14%","Ambiguous effect, k = 4, 19%")
subheader <- paste("MA26: Smith & Silva (k = 21)")
mycolors <- c("#FFFFFF","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA27, echo=FALSE}
# Tillman
dfma <- subset(df, meta=="Tillman")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 14, 74%","Not enough information, k = 2, 11%","Different effect, k = 2, 11%","Ambiguous effect, k = 1, 5%")
subheader <- paste("MA27: Tillman (k = 10)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA28, echo=FALSE}
# Toosi
dfma <- subset(df, meta=="Toosi")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 6, 30%","Not enough information, k = 4, 25%","Different effect, k = 5, 25%","Ambiguous effect, k = 5, 25%")
subheader <- paste("MA28: Toosi (k = 20)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA29, echo=FALSE}
# van Iddekinge
dfma <- subset(df, meta=="van Iddekinge")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 9, 90%","Ambiguous effect, k = 1, 10%")
subheader <- paste("MA29: van Iddekinge (k = 10)")
mycolors <- c("#FFFFFF","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA30, echo=FALSE}
# Webb
dfma <- subset(df, meta=="Webb")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 7, 35%","Not enough information, k = 4, 20%","Different effect, k = 5, 25%","Ambiguous effect, k = 4, 20%")
subheader <- paste("MA30: Webb et al. (k = 20)")
mycolors <- c("#FFFFFF","#FFFF00","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Cohen's d)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Cohen's d)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x=c(-0.1,3),y=c(-0.1,3)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA31, echo=FALSE}
# Webb
dfma <- subset(df, meta=="Woodin")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 6, 46%","Different effect, k = 5, 38%","Ambiguous effect, k = 2, 15%")
subheader <- paste("MA31: Woodin (k = 13)")
mycolors <- c("#FFFFFF","#FFa500","#FF0000")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Hedges' g)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Hedges' g)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  expand_limits(x=c(-0.25,2.5),y=c(-0.25,2.5)) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r MA32, echo=FALSE}
# Woodley
dfma <- subset(df, meta=="Woodley")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 4, 67%","Not enough information, k = 2, 33%")
subheader <- paste("MA32: Woodley (k = 6)")
mycolors <- c("#FFFFFF","#FFFF00")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```

```{r MA33, echo=FALSE}
# Yoon
dfma <- subset(df, meta=="Yoon")
dfma$discr <- factor(dfma$info)
#sum(dfma$info == 0);sum(dfma$info == 1);sum(dfma$info == 2);sum(dfma$info == 3)
levels(dfma$discr) = c("No discrepancy, k = 11, 100%")
subheader <- paste("MA33: Yoon et al. (k = 11)")
mycolors <- c("#FFFFFF")

ggplot(dfma, aes(x = effestnew.exp, y = effest.exp, col=discr)) + 
  geom_point(alpha = 0.9, size = 3, stroke=0.2) +
  theme_dark() +
  geom_abline() + 
  scale_shape(solid = FALSE) +
  theme(legend.justification = c(0.9, 0), legend.position = c(0.985, 0.02), legend.title=element_blank()) +
  scale_x_continuous("Reproduced effect sizes (Correlation r)", breaks=number_ticks(5)) +
  scale_y_continuous("Original effect sizes (Correlation r)", breaks=number_ticks(5)) + 
  scale_color_manual(values=mycolors) +
  ggtitle(subheader) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title=element_blank()) +
  annotate("text", x = -Inf, y = Inf, color="white", label = " Original MA effect size estimate = x \n Reproduced MA effect size estimate = x", hjust = 0, vjust=1)
```